### 2019-02-21 appendices/proofs.tex
fixed typo and some formatting stuff

  \case
    {$\userule{H-PassNext}$}
    {Given that
  $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$ and $\Sigma\infers s$,
  \refrule{T-Next} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1,s\handle{i}t_1',s'$ also preserves and thus
  $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$. By
  \refrule{T-Next} we now obtain that
  $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$. }

  \case
    {$\userule{H-FirstAnd}$}
    {Given that
  $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and
  $\Sigma\infers s$, \refrule{T-And} gives us that
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau_2$. By the induction hypothesis, we know
  that $t_1,s\handle{i}t_1',s'$ also preserves and thus
  $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Sigma\infers s'$. Therefore by
  \refrule{T-Next} we obtain
  $\Gamma,\Sigma\infers t_1'\And t_2:\Task(\tau_1\times\tau_2)$.}

  \case
    {$\userule{H-SecondAnd}$}
    {Given that
  $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and
  $\Sigma\infers s$, \refrule{T-And} gives us that
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau_2$. By the induction hypothesis, we know
  that $t_2,s\handle{i}t_2',s'$ also preserves and thus
  $\Gamma,\Sigma\infers t_2':\Task\tau_2$ and $\Sigma\infers s'$. Therefore by
  \refrule{T-Next} we obtain
  $\Gamma,\Sigma\infers t_1\And t_2':\Task(\tau_1\times\tau_2)$.}

  \case
    {$\userule{H-FirstOr}$}
    {Given that
  $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$,
  \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and
  $\Gamma,\Sigma\infers t_2:\Task\tau$. By the induction hypothesis we know that
  $t_1,s\handle{i}t_1',s'$ also preserves, and therefore
  $\Gamma,\Sigma\infers t_1':\Task\tau$ and $\Sigma\infers s'$. By
  \refrule{T-Or} we now obtain $\Gamma,\Sigma\infers t_1'\Or t_2:\Task\tau$.}

  \case
    {$\userule{H-SecondOr}$}
    {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
    By the induction hypothesis we know that $t_2,s\handle{i}t_2',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_2':\Task\tau$ and $\Sigma\infers s'$.
    By T-Or we now obtain $\Gamma,\Sigma\infers t_1\Or t_2':\Task\tau$.}

@@

\case{$e = e_1\Xor e_2$}
       {We normalise the two expressions first, $e_1,s\stride t_1,s'$, $e_2,s\stride t_2,s'$ and we can then be in two situations. One, we can have that $\Failing(t_1,s')$ and $\Failing(t_2,s')$ are both true. If that is so, then by definition, we have both $\Failing(e_1\Xor e_2,s)$ and no rule of the hanlding semantics applies, and therefore there exists no input for this case.\\
                                           Or we are in the situation where one or both of the two sub expressions does not fail. In that case, we know that $\Failing(e_1\Xor e_2,s)$ does not hold, and that at least one of the handling rules applies. Therefore, there must be an input $i$, namely $\Left$, $\Right$ or both.}

\case{$e = t_1\And t_2$}
       {We can again find ourselves in one of two situations. In the first case, both sub expressions fail, $\Failing(t_1,s)$ and $\Failing(t_2,s)$. In that case, we know that $\Failing(t_1\And t_2,s)$ also fails by definition. By the induction hypothesis, we know that for both $t_1$ and $t_2$ there is no input that can be handled. Since the only two rules for $\And$ that handle input just pass this input on to one of the two expressions, we know that indeed no $i$ applies.\\
                                           In the case that one or both sub expressions do not fail, then by definition $t_1\And t_2$ not failing under $s$. Again by induction hypothesis, we know that for one or both of the expressions, there exits an $i$ that can be handled. Then by H-FirstAnd and H-SecondAnd, we know that we can pass this $i$, by prefixing it with either $\First$ or $\Second$.}

\case{$e = t_1\Or t_2$}
       {We can again find ourselves in one of two situations. In the first case, both sub expressions fail, $\Failing(t_1,s)$ and $\Failing(t_2,s)$. In that case, we know that $\Failing(t_1\Or t_2,s)$ also fails by definition. By the induction hypothesis, we know that for both $t_1$ and $t_2$ there is no input that can be handled. Since the only two rules for $\Or$ that handle input just pass this input on to one of the two expressions, we know that indeed no $i$ applies.\\
                                           In the case that one or both sub expressions do not fail, then by definition $t_1\Or t_2$ not failing under $s$. Again by induction hypothesis, we know that for one or both of the expressions, there exits an $i$ that can be handled. Then by H-FirstOr and H-SecondOr, we know that we can pass this $i$, by prefixing it with either $\First$ or $\Second$.}

>>>>

\case{$\userule{H-PassNext}$}
     {Given that $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$.
     By \refrule{T-Next} we now obtain that $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$. }

\case{$\userule{H-FirstAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1'\And t_2:\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-SecondAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_2,s\handle{i}t_2',s'$ also preserves and thus $\Gamma,\Sigma\infers t_2':\Task\tau_2$ and $\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1\And t_2':\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-FirstOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_1,s\handle{i}t_1',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_1':\Task\tau$ and $\Sigma\infers s'$.
     By \refrule{T-Or} we now obtain $\Gamma,\Sigma\infers t_1'\Or t_2:\Task\tau$.}

\case{$\userule{H-SecondOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_2,s\handle{i}t_2',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_2':\Task\tau$ and $\Sigma\infers s'$.
     By T-Or we now obtain $\Gamma,\Sigma\infers t_1\Or t_2':\Task\tau$.}

@@

\case{$e = e_1\Xor e_2$}
     {We normalise the two expressions first, $e_1,s\stride t_1,s'$, $e_2,s\stride t_2,s'$ and we can then be in two situations.
     One, we can have that $\Failing(t_1,s')$ and $\Failing(t_2,s')$ are both true.
     If that is so, then by definition, we have both $\Failing(e_1\Xor e_2,s)$ and no rule of the handling semantics applies, and therefore there exists no input for this case.

     Or we are in the situation where one or both of the two sub expressions does not fail.
     In that case, we know that $\Failing(e_1\Xor e_2,s)$ does not hold, and that at least one of the handling rules applies.
     Therefore, there must be an input $i$, namely $\Left$, $\Right$ or both.}

\case{$e = t_1\And t_2$}
     {We can again find ourselves in one of two situations.
     In the first case, both sub expressions fail, $\Failing(t_1,s)$ and $\Failing(t_2,s)$.
     In that case, we know that $\Failing(t_1\And t_2,s)$ also fails by definition.
     By the induction hypothesis, we know that for both $t_1$ and $t_2$ there is no input that can be handled.
     Since the only two rules for $\And$ that handle input just pass this input on to one of the two expressions, we know that indeed no $i$ applies.

     In the case that one or both sub expressions do not fail, then by definition $t_1\And t_2$ not failing under $s$.
     Again by induction hypothesis, we know that for one or both of the expressions, there exits an $i$ that can be handled.
     Then by H-FirstAnd and H-SecondAnd, we know that we can pass this $i$, by prefixing it with either $\First$ or $\Second$.}

\case{$e = t_1\Or t_2$}
     {We can again find ourselves in one of two situations.
     In the first case, both sub expressions fail, $\Failing(t_1,s)$ and $\Failing(t_2,s)$.
     In that case, we know that $\Failing(t_1\Or t_2,s)$ also fails by definition.
     By the induction hypothesis, we know that for both $t_1$ and $t_2$ there is no input that can be handled.
     Since the only two rules for $\Or$ that handle input just pass this input on to one of the two expressions, we know that indeed no $i$ applies.

     In the case that one or both sub expressions do not fail, then by definition $t_1\Or t_2$ not failing under $s$.
     Again by induction hypothesis, we know that for one or both of the expressions, there exits an $i$ that can be handled.
     Then by H-FirstOr and H-SecondOr, we know that we can pass this $i$, by prefixing it with either $\First$ or $\Second$.}
